\documentclass[]{deedy-resume-pdflatex}

\begin{document}

\lastupdated

\namesection{Emanuel}{Joívo}{ \href{mailto:emanueljoivo@gmail.com}{emanueljoivo@gmail.com} 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{UFCG - Campina Grande}
\descript{BS in Computer Science}
\location{Jan 2016 - Dec 2023}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\location{ 
%CRA : 6.32 / 10.0\\ {\footnotesize{ similar to the GPA }}}
%\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 

Github:// \href{https://github.com/emanueljoivo}{\custombold{emanueljoivo}} \\
LinkedIn://  \href{https://www.linkedin.com/in/emanueljoivo}{\custombold{emanueljoivo}} 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming Languages}
\location{Expert:}
\textbullet{Golang} \\ 
\textbullet{Python} \\
\textbullet{Node.js} \\
\textbullet{Shell} \\
\textbullet{Java} \\
\textbullet{JavaScript} \\
\location{Proficient:}
\textbullet{C/C++} \\
\textbullet{TypeScript} \\
\textbullet{Haskell} \\
\sectionsep

\subsection{Tools \& Technologies}
\location{Expert:}
\textbullet{Kubernetes} \\
\textbullet{Terraform/Terragrunt} \\
\textbullet{Docker/Compose/Swarm} \\
\textbullet{AWS/GCP/Azure} \\
\textbullet{GitOps/FluxCD} \\
\textbullet{Ansible} \\
\textbullet{Git/Github/GitLab} \\
\location{Proficient:}
\textbullet{OpenStack} \\
\textbullet{Vagrant} \\
\textbullet{Spring Ecosystem} \\
\textbullet{VueJs} \\
\textbullet{Angular} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Anota Al}
\descript{| Senior DevOps Engineer}

\location{June 2025 - Present | Campina Grande, PB}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Engineered a next-generation WhatsApp chatbot platform and application lifecycle management solution, migrating from static Docker Compose to dynamic Kubernetes-based architecture for large-scale environments.
\item Architected and implemented a custom Kubernetes operator in Golang to automate the entire chatbot lifecycle, enabling seamless scaling and resource management.
\item Spearheaded SRE initiatives by creating and maintaining reusable Terraform modules for infrastructure provisioning, reducing deployment time by 60\%.
\item Orchestrated incident response and cloud account management to ensure 99.9\% availability and optimal performance of the chatbot system.
\item Collaborated with cross-functional teams to design and implement scalable, resilient architectures for the chatbot platform.
\item Optimized Kubernetes environment using Spot.io and Kubecost, achieving 40\% cost reduction while maintaining high reliability.
\end{tightemize}
\sectionsep

\runsubsection{Anota Al}
\descript{| DevOps Engineer}

\location{April 2024 - May 2025 | Campina Grande, PB}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Pioneered infrastructure automation and cloud-native solutions for WhatsApp chatbot platform.
\item Developed comprehensive monitoring and alerting systems to ensure system reliability and performance.
\end{tightemize}
\sectionsep

\runsubsection{Quimbik, Inc.}
\descript{| Infrastructure Consultant}

\location{March 2023 - August 2025 | Campina Grande, PB}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Engineered a Python orchestration layer integrating GitLab API with Terraform state files to automate customer onboarding and infrastructure deployment.
\item Architected and deployed Azure infrastructure modules supporting multi-tenant architecture, including networking (AGW, NSGs), computing (Kubernetes), and storage (MSSQL, failover groups).
\item Automated Windows machine provisioning and management using PowerShell scripts and Azure Desired State Configuration.
\item Implemented FluxCD with GitOps methodology for continuous deployment of .NET microservices, reducing deployment time by 70\%.
\item Deployed and managed Kubernetes clusters across Azure and AWS, supporting high-availability applications.
\item Developed CI/CD pipelines for Ruby on Rails microservices using GitHub Actions, streamlining the development workflow.
\end{tightemize}
\sectionsep

\runsubsection{Wildlife Studios}
\descript{| Site Reliability Engineer}

\location{February 2022 - December 2022 | Campina Grande, PB}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Architected and developed a comprehensive platform for Kubernetes cluster management, overseeing the full lifecycle of containerized environments.
\item Automated infrastructure provisioning across GCP and AWS using Infrastructure as Code (IaC) with Terraform, improving deployment consistency by 80\%.
\item Enhanced CI/CD pipelines with GitLab to streamline software delivery and reduce time-to-production.
\item Implemented comprehensive application visibility using Datadog and Logz, enabling proactive monitoring and faster incident resolution.
\item Managed critical incidents and maintained 99.95\% system availability across gaming infrastructure.
\end{tightemize}
\sectionsep

\runsubsection{Getup}
\descript{| Software Engineer}

\location{April 2021 - February 2022 | Campina Grande, PB}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Led full-cycle development and maintenance of the platform, from stakeholder feature discovery to production deployment.
\item Architected and developed the back-end, integrating with Cluster API for AWS and OpenStack, ensuring seamless cloud provider compatibility.
\item Spearheaded back-end and front-end integration coordination, aligning technical concepts with the Design System.
\item Enhanced end-to-end testing framework using Ginkgo and Gomega, improving test coverage by 45\% and ensuring production stability.
\end{tightemize}
\sectionsep

\runsubsection{Nuveo}
\descript{| Software Engineer}

\location{June 2020 - June 2021 | Campina Grande, PB}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Extended UltraOCR platform functionality by developing new API endpoints in Golang to support additional file types, increasing platform versatility.
\item Implemented OpenTelemetry for distributed tracing and metrics enrichment, providing deep insights into system behavior and performance.
\item Delivered technical presentations on microservices instrumentation and distributed systems traceability, sharing expertise with the development team.
\end{tightemize}
\sectionsep

\runsubsection{Distributed Systems Laboratory - UFCG}
\descript{| Site Reliability Researcher}

\location{October 2020 - March 2021 | Campina Grande, PB}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Contributed to advanced cloud environment research, investigating effective integration of Kubernetes platforms with OpenStack through OpenShift.
\item Operated key internal tools to ensure seamless project management and communication across research initiatives.
\end{tightemize}
\sectionsep

\runsubsection{VIRTUS - UFCG}
\descript{| Systems Administrator}

\location{December 2019 - October 2020 | Campina Grande, PB}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Architected and operated a private cloud environment using OpenStack, managing compute, storage, and networking resources for research infrastructure.
\item Developed a SaaS platform with Python and OpenStack, enabling scalable research computing services.
\item Conducted research and operational work on 5G infrastructure, including network performance testing and optimization.
\end{tightemize}
\sectionsep

\runsubsection{Distributed Systems Laboratory - UFCG}
\descript{| Software Engineer Intern}

\location{December 2018 - December 2019 | Campina Grande, PB}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Migrated legacy dashboard from AngularJS to VueJS, modernizing the user interface and improving performance.
\item Containerized systems across multiple programming languages, standardizing deployment processes.
\item Automated deployment workflows using Ansible, reducing manual configuration time by 70\%.
\item Architected back-end transitions to scalable microservices using Java and Golang, improving system maintainability.
\item Built observability tools and created dashboards with Grafana, enhancing system monitoring capabilities.
\item Presented technical findings at the Brazilian Symposium on Computer Networks and Distributed Systems (SBRC).
\end{tightemize}
\sectionsep
\end{minipage} 
\end{document}